\documentclass[12pt]{article}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{color}

\title{SE 3XA3: Problem Statement\\Garden Defender}

\author{Team 29
		\\ Ashley Williams, willia18
		\\ Declan Mullane, mullanem
		\\ Leo Shi, shiy12
}

\date{September 20, 2018}

%\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{12X}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Sept. 20 & Leo Shi & Initial Draft\\
Sept. 20 & Ashley Williams & Initial Draft\\
Sept. 20 & Declan Mullane & Initial Draft\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}


\newpage


\maketitle 

\section{What problem are you trying to solve?}

Game1 is a simple first person shooter built to be played on a PC. However, simple as it is, it still contains a few key flaws in its execution that make it a lackluster game. With only one character and one stage design, the game is unable to hold interest for long, especially as its default difficulty exceeds the average player's capabilities. This, compounded with the fact that the game lacks any form of instruction, makes it unfriendly to users. We plan to re-implement Game1 by adding a user guide to explain how to play the game, as well as stages with gradually increasing difficulty to make it more playable. With these changes, we hope to create a game that is both more user friendly as well as enjoyable, to keep players' interest and alleviate boredom. 

\section{Why is this an important problem?}
Everyone gets stressed out or suffers from boredom now and then.  A simple and intuitive game can be an effective means for relief from these everyday issues.  We also want to improve upon the existing game by making small changes.  For instance, the original game was designed to be downloaded and run on a computer.  We want to remove this hassle and  increase accessibility to the game by implementing it on a web browser. 

\section{What is the context of the problem you are solving?}

Garden Defender is suitable for players of all age groups. As a game built by JavaScript, it is compatible with most major web browsers and is able to run under Windows, MacOS and Linux. The Stakeholders of our project include ourselves as developers, as well as players of the game. It is the developers' concern to create a game that is both entertaining and compelling, so that the players will enjoy the game and want to continue playing it. The players will therefore be affected by the outcome of the project, as their boredom and stress is the problem to be solved by the re-implementation of Game1. 




%\wss{comment}

%\ds{comment}

%\mj{comment}

%\cm{comment}

%\mh{comment}

\end{document}